Quantum Interval-Valued Probability: Measurement and Probability

### 2017-11-07 prop_iop.tex
prop_iop.tex \subsection{Convexity and Core} Updating...

on some Hilbert space, and verify that there are no states that are

@@

Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
defined in Table~\ref{tab:non-Born-QIVPM}
\begin{table}
\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
on a Hilbert space of dimension~$d\ge3$. The projectors mapping
to the same interval are listed in the column labeled by $P$ and
separated by commas.}
\centering{}%
\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{i'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{i'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}

@@

$\ket{0}$, $\ket{\ps}$, and $\ket{\ps'}$ respectively. }

@@

The inner product of two distinguish states $\ket{i'}\ne\ket{j'}$
is $\ip{i'}{j'}=\frac{1}{4}\ne0$. Also, the inner product $\ip{i'}{0}=1/\sqrt{2}\ne0$.
Hence, a set of projections $\mathcal{S}=\left\{ \proj{0}\right\} \cup\set{}$.

@@

\item When $P_{0}=\proj{0}$, if $P_{1}=\proj{0}+P_{2}$, then equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})

@@

\item When $P_{1}=\mathbb{1}-\proj{0}$, we have

@@

={} & \bar{\mu}\left(\mathbb{1}-\proj{0}\right)+\bar{\mu}\left(\proj{0}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.

@@

\item When $P_{1}\ne\mathbb{1}-\proj{0}$, we have

@@

holds when $P_{0}=\proj{0}$. Similarly, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
holds when $P_{0}=\proj{\ps}$ or $P_{0}=\proj{\ps'}$. By lemma~\ref{lemma:quantum-convex-condition-lemma},

@@

also true when when $P_{0}=\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$,
or $\mathbb{1}-\proj{\ps'}$.

@@

for any~$P$, the state~$\rho$ must satisfy: 

@@

\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,

@@

which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. The last equation never holds proving the theorem.\end{proof}

>>>>

on the Hilbert space, and verify that there are no states that are

@@

Given two distinguish states $\ket{i'}\ne\ket{j'}$, since the inner
products $\ip{i'}{j'}$ and $\ip{i'}{0}$ are both non-zero, all projectors
in $\mathcal{S}=\left\{ \proj{0}\right\} \cup\set{\proj{i'}}{i=1,\ldots,d-1}$
are not commuting. Consider the function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
defined by 
\bar{\mu}\left(P\right)=\cases{ 
\imposs\,, & if $P=\mathbb{0}$ or $P\in\mathcal{S}$ ;\\ 
\necess\,, & if $P=\mathbb{1}$ or $\mathbb{1}-P\in\mathcal{S}$ ;\\ 
\unknown\,, & otherwise. 
}\label{eq:non-Born-QIVPM} \end{equation}

@@

$\ket{0}$, $\ket{1'}$, and $\ket{2'}$ respectively. }

@@

@@

\item When $P_{0}=\proj{\psi}\in\mathcal{S}$, if $P_{1}=\proj{\psi}+P_{2}$,
then equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})

@@

\item When $P_{1}=\mathbb{1}-\proj{\psi}$, we have

@@

={} & \necess+\imposs=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.

@@

\item When $P_{1}\ne\mathbb{1}-\proj{\psi}$, neither $P_{1}\in\mathcal{S}$
nor $\mathbb{1}-P_{1}\in\mathcal{S}$ because all projectors in $\mathcal{S}$
are not commuting. Hence,

@@

holds when $P_{0}=\proj{\psi}\in\mathcal{S}$. By lemma~\ref{lemma:quantum-convex-condition-lemma},

@@

also true when when $P_{0}=\mathbb{1}-\proj{\psi}$, where $\proj{\psi}\in\mathcal{S}$.

@@

for any~$P$, the state~$\rho$ must satisfy $\mu_{\rho}^{\mathrm{B}}(P)$
for all $P\in\mathcal{S}$. This implies 

@@

\ip{\phi_{j}}{0}=\ip{\phi_{j}}{i'}=0\label{eq:probability-zero-on-states}

@@

for all $i=1,\ldots d-1$ and for all $j=1,\ldots N$. Eq.~(\ref{eq:probability-zero-on-states})
never holds proving the theorem.\end{proof}
